Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-03-31 draft/paper1.tex
Paper split

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Halo of Massive Galaxies]{A Detection of the Environmental 
       Dependence of the Stellar Profiles and Halos of Massive Central Galaxies}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Kevin Bundy,$^{3,1}$
        Jenny Greene,$^{4}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Rachel Mandelbaum,$^{6}$
        Michael Strauss,$^{4}$
        and HSC collaboration$^{7}$   
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{6}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{7}$Another Department, Different Institution, Street Address, City Postal 
              Code, Country
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    For the first time, we conclusively show that at fixed stellar mass, massive central 
    galaxies display mass density profiles that are not self similar and which 
    present subtle but systematic differences that correlate with \mhalo{}. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent outer 
    envelopes. 
    These differences translate into a clear environmental dependence of the mass-size 
    relation: central galaxies in more massive halos have larger $R_{\mathrm{50}}$ 
    at fixed \mtot{}. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    Furthermore, because galaxies in larger halos have more extended envelopes, 
    the amount of light that is missed will be halo mass dependent. 
    Finally, at fixed total stellar mass, there is a large (but continuous) diversity 
    in the amplitude of stellar profiles at 100 kpc. 
    We argue that ``cD'' galaxies represent the tail end of a distribution and 
    are not a distinct class of massive galaxies. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_m100_m10_compare}
      \caption{
          Three-color images for a subsample of massive galaxies at $z{\sim}0.4$. 
          All of these galaxies have the same mass within a 10 kpc aperture 
          ($11.2<\log (M_{\star,10\ \mathrm{kpc}}/M_{\odot})<11.3$). 
          The dash-line circle at the top-left figure indicates 10 kpc.
          Galaxies are rank-ordered from top to bottom and from left to right by 
          their \mstar{} within a 100 kpc aperture which varies from $10^{11.2} M_{\odot}$ 
          to $10^{11.7} M_{\odot}$. 
          At fixed ``inner'' mass ($M_{\star,10}$), massive galaxies display significant
          diversity in their outer profiles. 
          Red boxes indicate galaxies in halos more massive than 
          ${\sim} 10^{14.0} M_{\odot}$. 
          }
      \label{fig:m100_m10_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    According to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''
    \footnote{There are different observational definitions of ``environment''. 
    In this paper, we use the term ``environment'' and halo mass interchangeably}.

    Previous work has shown that the half-light radii of massive ETGs is tightly 
    correlated with \mstar{} (e.g. \citealt{Shen2003, Guo2009}). 
    Models based on the ``two-phase'' formation scenario naturally predict that this 
    mass--size relation should exhibit an environmental dependence: the effective radii 
    of massive ETGs in more massive halos should be larger than those in less massive
    halos at fixed \mstar{} (e.g. \citealt{Shankar2013, Shankar2014}).

    However, while hints of an environmental dependence in the mass-size relation have 
    been spotted at high-$z$ (e.g. \citealt{Papovich2012, Lani2013, Delaye2014}; but 
    also see \citealt{Rettura2010}), there is no solid evidence for this effect at 
    low-$z$ (e.g. \citealt{Nair2010, HCompany13}; but also see \citealt{Yoon2017}). 
    The absence of an environmental dependence in the mass-size relation is an 
    outstanding challenge to the two-phase formation scenario of ETGs.

    From an observational perspective, we hypothesize that the lack of a detection of 
    this effect may be related a combination of the methodologies employed, as well as 
    the lack of deep high-quality imaging for large numbers of massive ETGs. 
    In particular, massive ETGs have very steep inner stellar density profiles, 
    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
    (e.g. \citealt{Bernardi2013, DSouza2014}), 
    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to revisit the 
    question of the environmental dependence in the mass-size relation. 
    The goal of this paper is to compare the \mden{} profiles and structural scaling 
    relations of massive central galaxies in both low and high mass dark matter halos. 
    Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample (${\sim} 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer.

@@

    Massive central galaxies in this work show an intriguing diversity on the plane 
    defined by these two metrics.  
    We preview this using Fig~\ref{fig:m100_m10_color}, which shows a subsample of 
    massive galaxies at $z{\sim} 0.4$ that share very similar value of \minn{}, but 
    exhibit a large diversity in their outer profiles. 
    Assuming that galaxies at fixed \minn{} share a similar in-situ formation history, 
    it is of great interest to investigate the relation between their present day halo 
    mass and the extend of their outer envelopes. 
    We note that although a circular aperture is shown on Fig~\ref{fig:m100_m10_color}, 
    for our mass measurements, we always use elliptical apertures that follow the 
    average isophotal shape. Finally, given our narrow mass and redshift range, we 
    can safely ignore significant mass growth and structural evolution in this work
    (no star formation, lower merger rate \etal~e.g.\ \citealt{Bellstedt2016},
    \citealt{Inagaki2015}; but also see \citealt{Bai2014}).

@@

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.

@@

    Our study focuses on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos.

    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    To ensure a clean separation in \mhalo{}, here we only focus on the central 
    galaxies of clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    We have checked that none of the results in this work depend on the choice of this 
    $\lambda$ limit. 
    For massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
%% ------------------------------------------------------------------------------------ %%

@@

    Based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
    live in a fairly broad range of halos masses.
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.

@@

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item \rbcg{} sample: we select a sample of 164 galaxies at 
            $0.3 \leq z \leq 0.5$ that are the central galaxies 
            in $\lambda > 30$ \redm{} clusters. 
            They represent the central galaxies in very massive halos 
            (\logmh{}$\geq 14.2$). 
        \item \nbcg{} sample: after excluding all cluster members from the 
            \texttt{hscZ} sample, we have 14661 bright galaxies at 
            $0.3 \leq z \leq 0.5$. 
            After applying an additional \mstar{} cut (see Section 
            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
            halos with \logmh{}$<14.0$.  
    \end{itemize}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_1}
      \caption{
          The environmental dependence of the stellar mass profiles of massive central 
          galaxies. 
          The left panel corresponds to samples matched by ``total'' stellar mass 
          (\mtot{}). 
          The right panel corresponds to samples matched by ``core-mass'' (\minn{}). 
          Orange and red lines correspond to central galaxies living in halos with 
          \logmh{} $\geq 14.2$. 
          Black and grey correspond to central galaxies living in halos with 
          \logmh{} $\leq 14.0$. 
          Thin lines show the profiles of individual galaxies while thick lines show 
          the median profile. 
          The uncertainty on the median profile is given by the shaded region and is 
          computed via bootstrap resampling. 
          The brown line in the bottom panels show the relative difference between 
          two median profiles 
          ($\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
          \log(\mu_{\star, \mathrm{cenLowMh}})$). 
          Errors on the difference between the two profiles is computed via bootstrap 
          too. 
          The grey shaded regions show a Monte Carlo test to asses how likely is it to 
          obtain $\Delta$ from random sub-samples of the data. 
          To compute the grey shaded regions, we first mix the two samples 
          (\rbcg{} and \nbcg{}), then draw sub-samples of galaxies from the mixed 
          population and compute $\Delta$ in the same fashion as for our fiducial signal. 
          We repeat this process 5000 times.  
          The dark-grey shaded region (light-grey shaded region) shows the 1-$\sigma$ 
          (3-$\sigma$) fluctuations in $\Delta$ from these 5000 draws.
          }
      \label{fig:prof_1} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
    completeness of our HSC samples.

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We compute \mstar{} values for these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
    \texttt{S82-MGC} with the SMFs of galaxies from our two 
    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
    The \rbcg{} sample is less affected by completeness because we can utilize 
    photo-$z$s from \redm{}. 
    However, the completeness of the \nbcg{} sample is still limited by the 
    availability of spec-$z$s from BOSS.

    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
    where our two samples are complete. 
    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    Please see the next section and Appendix~\ref{app:match} for more details.
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\subsubsection{Environmental Dependence of the Profiles of Massive Galaxies}
    \label{sssec:sbp_mtot}

    We now ask whether or not galaxies from our sample have \mden{} profiles that 
    depend on \mhalo{} (at fixed \mstar{}). 
    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
    carefully matched in \mstar{} and redshift using a KDTree algorithm 
    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
    \mden{} profiles from both samples are impacted by seeing and background subtraction 
    at similar levels. 
    To match the two samples by stellar mass, we will use two different methods:

>>>>

% Commenting:
\newcommand{\xxx}[1]{\textcolor{red}{\textbf{XXX}}}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{TODO:~#1}}}
\newcommand{\plan}[1]{\textcolor{cyan}{#1}}
\newcommand{\addref}{{\textcolor{red}{REF}}}
\newcommand{\note}[2]{\textcolor{blue}{\textbf{[Comment (#1): #2]}}}
\newcommand{\song}[1]{\textcolor{magenta}{\textbf{[Song: #1]}}}
\newcommand{\alexie}[1]{\textcolor{blue}{\textbf{[Alexie: #1]}}}
\newcommand{\jenny}[1]{\textcolor{Bittersweet}{\textbf{[Jenny: #1]}}}
\newcommand{\kevin}[1]{\textcolor{green}{\textbf{[Kevin: #1]}}}
\newcommand{\update}[1]{\textcolor{Bittersweet}{#1}}
%\newcommand{\update}[1]{#1}

@@

%% ------------------------------------------------------------------------------------ %% 
\title[Structure and Halo of Massive Galaxies]{Tracing the Stellar Halo of Massive 
       Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam}

\author[S. Huang et al.]{
        Song Huang,$^{1,2}$\thanks{E-mail: song.huang@ipmu.jp (SH)}
        Alexie Leauthaud,$^{2,1}$
        Jenny Greene,$^{4}$
        Kevin Bundy,$^{3,1}$
        Yen-Ting Lin,$^{5}$
        \newauthor
        Masayuki Tanaka,$^{6}$
        Rachel Mandelbaum,$^{7}$
        Satoshi Miyazaki,$^{5,8}$
        HSC collaboration 
        \\
        $^{1}$Kavli-IPMU, The University of Tokyo Institutes for Advanced Study, 
              the University of Tokyo (Kavli IPMU, WPI), Kashiwa 277--8583, Japan\\
        $^{2}$Department of Astronomy and Astrophysics, University of California 
              Santa Cruz, 1156 High St., Santa Cruz, CA 95064, U.S.A\\
        $^{3}$UCO/Lick Observatory, University of California, Santa Cruz,
              1156 High Street, Santa Cruz, CA 95064, USA\\
        $^{4}$Department of Astrophysical Sciences, Peyton Hall,
              Princeton University, Princeton, NJ 08540, USA \\
        $^{5}$National Astronomical Observatory of Japan, 2--21--1 Osawa, Mitaka, 
              Tokyo 181--8588, Japan\\
        $^{6}$Academia Sinica Institute of Astronomy and Astrophysics, 
              P.O. Box 23--141, Taipei 10617, Taiwan\\
        $^{7}$McWilliams Center for Cosmology, Department of Physics, 
              Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
        $^{8}$SOKENDAI (The Graduate University for Advanced Studies), Mitaka,
              Tokyo, 181--8588, Japan
        }   
%% ------------------------------------------------------------------------------------ %% 
\date{Accepted XXX. Received YYY; in original form ZZZ}        
\pubyear{2017}

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$ \sb{} in $i$-band), high-quality 
    (0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    Our sample consists of ${\sim}7000$ massive (\mstar{}$\geq 11.5$) central galaxies 
    at $0.3 < z < 0.5$. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking. 
    Shallow imaging will miss light at the outskirts of galaxies and this has an 
    important impact on measurements of the galaxy mass function. 
    With these deeper data, we show definitively that at fixed stellar mass,
    massive central galaxies display mass density profiles that are not self similar, 
    with the accreted fraction increasing towards unity for galaxies in our highest 
    stellar mass bin. 
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems. 
    Our mass profiles are provided in a convenient tabulated format in order to 
    facilitate comparisons with predictions from numerical simulations of galaxy 
    formation.

@@

@@

    {\bf PP here about mass dependence: in the simulations, a larger fraction of the mass 
    is ex-situ at increasingly higher mass. Can we see evidence for that observationally by 
    looking at light profiles?}

    In addition, according to this two-phase formation scenario, the late time growth of massive ETGs 
    is intrinsically tied to the growth of their host dark matter halos 
    (e.g. \citealt{Leauthaud2012, Behroozi2013, Shankar2013}). 
    Massive ETGs that live at the center of more massive halos should experience 
    a different mass assembly history and should be subject to a larger merger rate 
    compared to ETGs that live in smaller dark matter halos. 
    A natural prediction of the two-phase formation scenario is therefore that the 
    structural properties of massive galaxies should depend on their ``environment''

    In order to truly understand the build-up of the outer parts of massive galaxies, very 
    deep data are needed. Massive ETGs have very steep inner stellar density profiles, 
    extremely extended stellar envelopes, and radial-dependent isophotal shapes which 
    make accurate measurements of \mstar{} and $R_{\mathrm{e}}$ very challenging
    (e.g. \citealt{Bernardi2013, DSouza2014}), 
    especially in the presence of shallow imaging data such as the Sloan Digital Sky 
    Survey (SDSS; e.g. \citealt{SDSSDR7, SDSSDR12}).

    In this paper, we take advantage of new high-resolution (median 
    FWHM${\sim} 0.6^{\arcsec}$ in $i$-band) and deep ($i$-band surface brightness 
    limit $> 28.5$\sb) imaging from the Hyper-Suprime Cam (HSC) Subaru Strategic 
    Program \citep[SSP,][]{HSCDR1} to characterize the outer parts of massive galaxies 
    as a function of their properties. Here we will focus on (a) showing that we can 
    measure profiles for galaxies out to 100 kpc reliably with the HSC data and (b) looking at 
    trends in stellar mass and outer envelope properties. In a second paper in this series, we 
    will directly show the environmental dependence of the outer envelope mass.
    %The goal of this paper is to compare the \mden{} profiles and structural scaling 
    %relations of massive central galaxies in both low and high mass dark matter halos. 
    %Fig~\ref{fig:sdss_compare} displays a comparison of the imaging quality of massive 
    %ETGs using SDSS versus using the new HSC data. 
    The deep imaging depth and excellent seeing conditions of HSC images make them 
    perfect for mapping the \mstar{} distributions of massive galaxies out to very 
    large radii. 
    With the help of the \redm{} cluster catalog (e.g.\ \citealt{Rykoff2014}; 
    \citealt{Rozo2015b}; please see Section~\ref{ssec:redmapper} for details), we 
    select a large sample (${\sim} 15000$) of massive central 
    galaxies with $0.3 < z < 0.5$ using ${\sim} 100$ square degree of data from the 
    HSC wide layer.

@@

    {\bf We will show the implications for the stellar mass function of including most of 
    the stellar light, a task that has been complicated before now due to shallower data. 
    We will also investigate the idea that the accreted fraction is a function of stellar mass.}

@@

    In the end, at $0.3 \leq z \leq 0.5$, we gather a sample of 25286 galaxies with 
    reliable redshift information (will be referred as \texttt{hscZ}).
    %% Saved as "dr1_wide_galaxy_icmodel_21.5.fits"
    Among them, the BOSS and SDSS ``legacy'' LRG samples provide the majority of 
    spec-$z$. 
    By comparing with the Stripe 82 Massive Galaxy Catalog
    (\texttt{S82-MGC}; \citealt{Bundy2015}), \citet{Leauthaud2016} have measured the
    \mstar{} completeness of the combined BOSS and SDSS samples. 
    They estimate that the BOSS spec-$z$ sample is about 80\% complete at 
    \logms{}$\geq 11.6$ at $0.3 < z < 0.5$. 
    The GAMA survey, which partially overlaps with the HSC footprints, supplements 
    our \texttt{hscZ} sample by 14\%. 
    Based on \citet{Taylor2011} (e.g.\ their Fig~~6), at $z{\sim} 0.3$, the GAMA 
    sample is 80\% complete down to $10^{10.8}$\msun; but only 80\% complete to 
    $10^{12.0}$\msun at $z{\sim} 0.5$. 
    We can therefore expect our sample to be roughly \mstar{}-complete above 
    \logms{}$\geq 11.5$-$11.6$. 
    This question will be addressed more carefully using the overlap region between 
    HSC and the \texttt{S82-MGC} in Section \ref{ssec:s82}.
    {\bf Seems to have the section wrong? Plus, can we consolidate these discussions?}

@@

    For now, we wish to focus on galaxies located at the center of their dark matter halos. 
    To limit our sample to central galaxies, we use \texttt{v5.10} of the \redm{}{} 
    cluster catalog\footnote{See: http://risa.stanford.edu/redmapper/} 
    (e.g.\ \citealt{Rykoff2014}; \citealt{Rozo2015b}). 
    These authors have developed a well-tested red-sequence cluster finder that has 
    been run on SDSS DR8 (\citealt{SDSSDR8}) photometric data. 
    For each cluster, the catalog provides a photometric redshift ($z_{\lambda}$), a 
    cluster richness ($\lambda$), and identifies the most likely central galaxy (the 
    galaxy with the highest $P_{\mathrm{Cen}}$ value). 
    The \redm{}{} catalog also provides a list of member galaxies for each cluster and 
    their associated membership probabilities. 
    Details about the performance of the \redm{}~cluster catalog can be found in 
    \citet{Rozo2014}, \citet{Rozo2015a}, and \citet{Rozo2015b}. 
    Several studies have published calibrations between the \redm{}~richness estimate, 
    $\lambda$, and halo mass (e.g.\ \citealt{Saro2015, Farahi2016, Simet2016, 
    Melchior2016}). 
    All these studies consistently find that \redm{} clusters with $\lambda > 20$ 
    have $\log (M_{\mathrm{halo}}/M_{\odot}) \geq 14.0$. 
    The \redm{} catalog therefore helps us group massive central galaxies into 
    samples with different average \mhalo{}. 
    We will use the central galaxies of \redm{} clusters 
    ($P_{\mathrm{CEN}} \geq 0.7$) to form a sample of massive central galaxies that 
    live in massive halos.
%% ------------------------------------------------------------------------------------ %%

@@

    One of the goals of our work is to investigate the halo dependence of the outer 
    envelope. Although there is a correlation between $M_{\star}$ and $M_{\mathrm{Halo}}$,
    based on recent constraints of $M_{\star}$-$M_{\mathrm{Halo}}$ relation 
    (e.g.\ \citealt{Leauthaud2012}, \citealt{Behroozi2013}, \citealt{Kravtsov2014}), 
    even though our sample selects very massive galaxies (\logms{}$\geq 11.5$), they 
    With the help of the \redm{} catalog, we can broadly separate our sample into two
    groups with \logmh{}$<14.0$ and \logmh{}$>14.2$.
    live in a fairly broad range of halos masses.

@@

    Due to the depth and resolution of SDSS, the \redm{} catalog becomes slightly 
    incomplete at lower richness ($\lambda < 40$) at $z > 0.33$. 
    To ensure a clean separation in \mhalo{}, here we only focus on the central 
    galaxies of clusters with $\lambda > 30$. 
    According to \citet{Simet2016}, this $\lambda \geq 30$ sample should correspond to 
    $M_{\mathrm{halo}}>10^{14.2} M_{\odot}$. 
    We have checked that none of the results in this work depend on the choice of this 
    $\lambda$ limit. 
    For massive central galaxies that are not in these cluster-level halos, 
    we unfortunately can not estimate their \mhalo{} individually, but it is safe 
    to assume they will have $\log (M_{\mathrm{halo}}/M_{\odot}) < 14.0$.  
    {\bf I am still a bit confused why stellar mass completeness depends on Mh??}

@@

    \begin{itemize}
        \item \texttt{hscPho} sample: this parent sample consists of bright galaxies 
            with $i_{\mathrm{cModel}} \leq 21.0$, good quality imaging, and reliable 
            \texttt{cModel} photometry in all five HSC bands in the \texttt{S15B} 
            data release. 
        \item \texttt{hscZ} sample: we limit the \texttt{hscPho} sample to galaxies 
            with reliable redshift information. 
        \item {\bf Select only central galaxies using RedMapper: total number in full 
        sample?}
        \item We further divide the sample into an \rbcg{} sample and a \nbcg{} sample, 
          with the former roughly having \logmh{}$\geq 14.2$ and the latter having 
           \logmh{}$<14.0$.

%          : we select a sample of 164 galaxies at 
%            $0.3 \leq z \leq 0.5$ that are the central galaxies 
%            in $\lambda > 30$ \redm{} clusters. 
%            They represent the central galaxies in very massive halos 
%            (\logmh{}$\geq 14.2$). 
%        \item \nbcg{} sample: after excluding all cluster members from the 
%            \texttt{hscZ} sample, we have 14661 bright galaxies at 
%            $0.3 \leq z \leq 0.5$. 
%            After applying an additional \mstar{} cut (see Section 
%            \ref{ssec:isedfit}), this sample corresponds to central galaxies in 
%            halos with \logmh{}$<14.0$.  
    \end{itemize}

@@

@@

    {\bf Still worth thinking about where this belongs and if it can be consolidated with the 
    previous discussion somehow. Maybe better in results?}
    With the help of the \texttt{S82-MGC} (\citealt{Bundy2015}), we investigate the 
    \mstar{} completeness of our samples. 
    The \texttt{S82-MGC} sample matches the deeper SDSS photometric data in the 
    Stripe 82 region (\citealt{Annis2014}) with the near infrared data from the United 
    Kingdom Infrared Telescope Infrared Deep Sky Survey (UKIDSS; \citealt{Lawrence2007}). 
    The deeper photometry and better photo-$z$s make the \texttt{S82-MGC} sample complete 
    to \logms{}$\geq 11.2$ at $z<0.7$ which makes it sufficient to evaluate the 
    completeness of our HSC samples.

    There are 20453 \texttt{S82-MGC} galaxies that are also in the \texttt{hscPho} 
    sample at $0.3 \leq z_{\mathrm{s82}} \leq 0.5$. 
    We compute \mstar{} values for these galaxies using our fiducial 
    procedure\footnote{The \mstar{} using HSC photometry is in excellent with the 
    values derived from the \texttt{S82-MGC} which includes NIR data from UKIDSS; 
    \texttt{S82-MGC} also uses \texttt{iSEDFit} with similar assumptions.}. 
    The right side of Fig~\ref{fig:smf1} compares the SMFs of galaxies from 
    \texttt{S82-MGC} with the SMFs of galaxies from our two 
    samples\footnote{Errors on the SMFs are estimated via bootstrap resampling}. 
    Based on Fig~\ref{fig:smf1}, we conclude that our sample of massive galaxies is 
    reasonably complete down to \logms{}${\sim} 11.6$ at $0.3 \leq z \leq 0.5$. 
    %The \rbcg{} sample is less affected by completeness because we can utilize 
    %photo-$z$s from \redm{}. 
    %However, the completeness of the \nbcg{} sample is still limited by the 
    %availability of spec-$z$s from BOSS.    
    In this work, we will focus on the range $11.6 \le$ \logmtot{}$ \le 11.9$ 
    where our two samples are complete. 
    %When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    %samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    %Please see the next section and Appendix~\ref{app:match} for more details.
%% ------------------------------------------------------------------------------------ %%

@@
